### 2021-04-22 input/background.tex
add ref in section2

Numerous studies addressed content indexing in geo-distributed
infrastructures ranging from centralized services to fully
decentralized approaches~\REF. We advocate for the latter where
\processes host the service themselves so they do not need to request
remote -- possibly far away third-party -- entities to retrieve their
content location.  In this paper, we tackle the content indexing issue
as a dynamic logical partitioning problem. This section motivates this
shift and explains the shortcomings of existing implementations.

@@

Figure~\ref{fig:partition_intuition} depicts an infrastructure
comprising 17 interconnected \processes spread across France. In
Figure~\ref{fig:partition_intuitionA}, a single \Process~$R$ hosts the
content, so every other \process downloads from this \process when it
needs it. In that regard, \Process~$R$ only needs to disseminate a
message notifying all other \processes of its new content. \Process~$R$
can use uniform reliable broadcast~\REF and epidemic propagation~\REF
to guarantee that
\begin{inparaenum}[(i)]
\item every \process eventually knows the content location
\item by efficiently using neighbor-to-neighbor communication.
\end{inparaenum}

@@

Every \process ends up with at least one known replica that is its
closest. The set of interconnected \processes with the same closest
replica is a \emph{partition}. Every \process belongs to one, and only
one, partition. Contrarily to membership protocols that choose
neighboring \processes to communicate with based on metrics~\REF,
\processes in our context have no control over their neighboring
\processes: they cannot add nor remove communication links.

>>>>

Numerous studies addressed content indexing in geo-distributed
infrastructures ranging from centralized services to fully
decentralized approaches~\cite{squirrel}. We advocate for the latter where
\processes host the service themselves so they do not need to request
remote -- possibly far away third-party -- entities to retrieve their
content location.  In this paper, we tackle the content indexing issue
as a dynamic logical partitioning problem. This section motivates this
shift and explains the shortcomings of existing implementations.

@@

Figure~\ref{fig:partition_intuition} depicts an infrastructure
comprising 17 interconnected \processes spread across France. In
Figure~\ref{fig:partition_intuitionA}, a single \Process~$R$ hosts the
content, so every other \process downloads from this \process when it
needs it. In that regard, \Process~$R$ only needs to disseminate a
message notifying all other \processes of its new content. \Process~$R$
can use uniform reliable broadcast~\cite{hadzilacos1994modular} and epidemic propagation~\cite{epidemic-protocol}
to guarantee that
\begin{inparaenum}[(i)]
\item every \process eventually knows the content location
\item by efficiently using neighbor-to-neighbor communication.
\end{inparaenum}

@@

Every \process ends up with at least one known replica that is its
closest. The set of interconnected \processes with the same closest
replica is a \emph{partition}. Every \process belongs to one, and only
one, partition. Contrarily to membership protocols that choose
neighboring \processes to communicate with based on metrics~\cite{t-man},
\processes in our context have no control over their neighboring
\processes: they cannot add nor remove communication links.

### 2021-04-22 input/figpartitionintuition.tex
add ref in section2

\begin{figure*}
\centering
\subfloat[\Process~$R$ efficiently advertises its content using epidemic propagation. Every \process requests $R$ if needed.\label{fig:partition_intuitionA}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-1.png}}
\hfill
\subfloat[\Process $G$ creates a second replica splitting the red set in two. \Processes request their closest replica host.\label{fig:partition_intuitionB}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-2.png}}\hfill
\subfloat[\Process $B$ creates another replica. \Process~$B$ needs to notify only a small subset of \processes.\label{fig:partition_intuitionC}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-3.png}}\hfill
\subfloat[\Process $G$ destroys its replica. \Processes that belong to its partition must find the closest partition they are in.\label{fig:partition_intuitionD}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-4.png}}
%
\caption{The french RENATER topology. Partitions
  grow and shrink depending on creations and removals of
  replicas.} \label{fig:partition_intuition}
\end{figure*}

>>>>

\begin{figure*}
\centering
\subfloat[\Process~$R$ efficiently advertises its content using epidemic propagation. Every \process requests $R$ if needed.\label{fig:partition_intuitionA}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-1.png}}
\hfill
\subfloat[\Process $G$ creates a second replica splitting the red set in two. \Processes request their closest replica host.\label{fig:partition_intuitionB}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-2.png}}\hfill
\subfloat[\Process $B$ creates another replica. \Process~$B$ needs to notify only a small subset of \processes.\label{fig:partition_intuitionC}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-3.png}}\hfill
\subfloat[\Process $G$ destroys its replica. \Processes that belonged to its partition must find the closest partition they are in.\label{fig:partition_intuitionD}]{\includegraphics[trim=6cm 0.33cm 6cm 0.33cm, clip, width=0.24\textwidth]{img/Dynamic-partitioning-4.png}}
%
\caption{The french RENATER topology. Partitions
  grow and shrink depending on creations and removals of
  replicas.} \label{fig:partition_intuition}
\end{figure*}
